---
title: "August Data Collection Pt. 2"
author: "Anna Matthei and Gabriel Yossick"
date: "8/23/2023"
output:
  html_document:
    theme: readable 
    highlight: espresso
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
# Set knitr options
knitr::opts_chunk$set()
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(infer))
suppressPackageStartupMessages(library(modelr))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(tinytex))
# Read in demographics
global_slavery <- read.csv('Global_Slavery_Index.csv')
global_transplants <- read.csv('GODT_Global_Kidney_Transplant.csv')
poverty_gap <- read.csv('OECD_Poverty_Gap.csv')
poverty_rate <- read.csv('OECD_Poverty_Rate.csv')
organized_crime <- read.csv('Organized_Crime_Index.csv')
surgeon_workforce <- read.csv('Surgeon_Workforce.csv')
gini_index <- read.csv('WB_Gini_Index.csv')
working_poverty <- read.csv('Working_POverty_ILO.csv')

# Read in Formal Supply Chain Data
sexcountry <- read.csv("ILO_inflows_sexcountry.csv")
edu <- read.csv("ILO_education.csv")
outdest <- read.csv("ILO_outflow_destination.csv")
outwork <- read.csv("ILO_outside_workforce.csv")
skill <- read.csv("ILO_skill_level.csv")
trade_agreements <- readxl::read_xlsx("ILO_trade_agreements.xlsx")
unemploy <- read.csv("ILO_unemployment.csv")
WB_FDI <- read.csv("WB_FDI.csv")
OECD_FDI <- readxl::read_xlsx("OECD_FDI.xlsx")

# Read in Informal Supply Chain Data

#checkbox

checkbox <- function(id, label) {
  shiny::tagList(
    shiny::checkboxInput(id, label = NULL),
    shiny::tags$label(label, `for` = id)
  )
}
checkbox1 <- checkbox("Keep?", "Keep?")
```

# Introduction

This week we have added onto our demographics data, cleaned our formal/informal supply chain data, and did more qualitative research on kidney trafficking. Below we have listed our newly cleaned data, the additions to demographics, and our qualitative research. 

# Formal Supply Chain Data

The following data includes new data collect this week, but also some cleaned data sets from last week. We also have included numerous datasets from various databases that need to be confirmed on whether they are needed for the study. 

[International Monetary Fund Data Page](https://data.imf.org/?sk=388dfa60-1d26-4ade-b505-a05a558d9a42&sid=1479329132316)
The following are different datasets from the IMF that might be useful for the study:

[Balance of Payments](https://data.imf.org/?sk=7a51304b-6426-40c0-83dd-ca473ca1fd52)
The balance of payments is a statistical statement that summarizes transactions between residents and nonresidents during a period. It consists of the goods and services account, the primary income account, the secondary income account, the capital account, and the financial account. File is too big to attach to this document.
```{r}
checkbox1
```

[Commodity Terms of Trade](https://data.imf.org/?sk=2cddccb8-0b59-43e9-b6a0-59210d5605d2)
Country-specific commodity price indices, including export, import, and terms-of-trade indices. For each country, the change in the international price of up to 45 individual commodities is weighted using commodity-level trade data. Coverage includes 182 countries. Goes back to 1980.
```{r}
checkbox1
```

[Consumer Price Index (CPI)](https://data.imf.org/?sk=4ffb52b2-3653-409a-b471-d47b46d904b5)
Index numbers that measure changes in the prices of goods and services purchased or otherwise acquired by households, which households use directly, or indirectly, to satisfy their own needs and wants.This data was collected by the IMF and OECD.
```{r}
checkbox1
```

[Coordinated Direct Investment Survey(CDIS)](https://data.imf.org/?sk=40313609-F037-48C1-84B1-E1F1CE54D6D5)
The CDIS database presents detailed data on "inward" direct investment positions (i.e., direct investment into the reporting economy) cross-classified by economy of immediate investor, and data on "outward" direct investment positions (i.e., direct investment abroad by the reporting economy) cross-classified by economy of immediate investment. 
```{r}
checkbox1
```

[Coordinated Portfolio Investment Survey (CPIS)](https://data.imf.org/?sk=B981B4E3-4E58-467E-9B90-9DE0C3367363)
The CPIS is a voluntary data collection exercise conducted under the auspices of the IMF. An economy provides data on its holdings of portfolio investment securities (data are separately requested for equity and investment fund shares, long-term debt intruments, and short-term debt instruments).
```{r}
checkbox1
```

[Direction of Trade Statistics (DOTS)](https://data.imf.org/?sk=9d6028d4-f14a-464c-a2f2-59b2cd424b85)
DOTS presents the value of merchandise exports and imports disaggregated according to a country's primary trading partners. Area and world aggregates are includes in the display of trade flows between major areas of the world. Reported data is supplemented by estimates whenever such data is not available or current. 
```{r}
checkbox1
```

[Export Diversification and Quality](https://data.imf.org/?sk=a093df7d-e0b8-4913-80e0-a07cf90b44db)
Includes time series information. 
```{r}
checkbox1
```

[Financial Access Survey (FAS)](https://data.imf.org/?sk=388dfa60-1d26-4ade-b505-a05a558d9a42&sid=1479329132316)
Cibtaubs 180 time series and 65 indicators that are expressed as rations to GDPp, land area, or adult population to facilitate cross-economy comparisons. Provision of FAS data is voluntary.
```{r}
checkbox1
```

[Total Tariff Lines](https://wits.worldbank.org/CountryProfile/en/country/by-country/startyear/LTST/endyear/LTST/tradeFlow/Import/indicator/AHS-TTL-TRFF-LNS/partner/WLD/product/Total)
A dataset that contains information about the total number of tariff lines for specific products categorized using the Harmonized System, and this data is presented by country, providing insights into the tariff treatment of various goods in international trade.
```{r}
checkbox1
```


##Labor migration
The following is the cleaned dataset for the various ILO labor migration datasets.

**Inflow of working age foreign citizens by sex and country of citizenship**
```{r}
print(colnames(sexcountry))
checkbox1
```
The data on the inflow of working-age foreign citizens allows us to identify regions or countries that are more likely to be sources of potential kidney donors.

**Inflow of worker-age population by education and sex**
```{r}
print(colnames(edu))
checkbox1
```
Data on education level of incoming working migrants. This level of data might be useful to see patterns on education and kidney divulgence within the scope of the project. Includes all levels of education, which provides high utility.

**Inflow of employed foreign-born by occupation**
```{r}
print(colnames(skill))
checkbox1
```
Shows country of destination and national’s homestate.

**Outflow of nationals**
```{r}
print(colnames(outdest))
checkbox1
```
Data on the number of people working and living outside of society might be useful for predicting which and how many groups of people might be susceptible to organ trafficking.

**Persons outside the workforce**
```{r}
print(colnames(outwork))
checkbox1
```
Data on the number of people working and living outside of society might be useful for predicting which and how many groups of people might be susceptible to organ trafficking.

**Unemployment % sex, education, citizenship**
```{r}
print(colnames(unemploy))
checkbox1
```
Unemployment data might be indicative of possible susceptive populations. It can show domestic workforce strength, which might influence worker reliance on donating kidneys. 

**Trade agreement dataset**
```{r}
print(colnames(trade_agreements))
checkbox1
```
Labor provisions in trade agreements.

### Visas

show info on visa csvs and links to original source

### Foregin Direct Investments (FDI)

World Bank FDI Dataset
```{r}
WB_FDI2 <- pivot_longer(WB_FDI, starts_with("x"), 
                        names_to = "year",
                        values_to = "value")
print(colnames(WB_FDI2))
checkbox1
```
OECD FDI Dataset
```{r}
print(colnames(OECD_FDI))
##this data will suck to clean
checkbox1
```

# Informal Supply Chain Data

Short intro on this data

### flora/fauna trafficking

info and link

# Qualitative Research

More information on kidney trafficking through reports and case studies. Add links and screenshots

# Research Articles